A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2014-06-10 jacobian_calc_CMAME.tex
Address item 18

where $\phi$ is a constant truss angle, $AE$ is the axial rigidity of the truss, $L_{0}$ is original truss member length, $k_{s}$ is the Hooke's constant for the spring attached to the truss member, and $P$ is the applied load. $\phi$ is considered constant for small displacement for initial truss angles close to zero. For a demonstration and verification of each of the methods as well as a convergence rate study, this truss and spring model was analyzed with each of the methods and compared with the analytic solution. As in the reference \cite{rezaiee2010dynamic}, equilibrium solutions for 12 incremental load steps of $\Delta P=\SI{4.448}{\newton}$ were found. Solver parameters common to all tests were a maximum limit of 100 iterations for convergence, and a convergence tolerance for the change in displacement over an iteration $\Delta D \le \SI{1e-9}{\meter}$.  Data collected included number of iterations to converge summed over all load-steps and final displacement $D$, after the final load-step. Additionally finite difference and complex-step step sizes were varied in order to measure the impact on each of the approximate tangent-stiffness calculation methods. Naturally, varying the step size does not affect AD or the analytically derived tangent-stiffness since those are not functions of the step size. The accuracy results for verifying the tangent-stiffness calculation methods are summarized in Table~\ref{tab:ConvergenceStudy}. 

>>>>

where $\phi$ is a constant truss angle (a modeling decision made in \cite{rezaiee2010dynamic} that we mimic for consistency), $AE$ is the axial rigidity of the truss, $L_{0}$ is original truss member length, $k_{s}$ is the Hooke's constant for the spring attached to the truss member, and $P$ is the applied load. $\phi$ is considered constant for small displacement for initial truss angles close to zero. For a demonstration and verification of each of the methods as well as a convergence rate study, this truss and spring model was analyzed with each of the methods and compared with the analytic solution. As in the reference \cite{rezaiee2010dynamic}, equilibrium solutions for 12 incremental load steps of $\Delta P=\SI{4.448}{\newton}$ were found. Solver parameters common to all tests were a maximum limit of 100 iterations for convergence, and a convergence tolerance for the change in displacement over an iteration $\Delta D \le \SI{1e-9}{\meter}$.  Data collected included number of iterations to converge summed over all load-steps and final displacement $D$, after the final load-step. Additionally finite difference and complex-step step sizes were varied in order to measure the impact on each of the approximate tangent-stiffness calculation methods. Naturally, varying the step size does not affect AD or the analytically derived tangent-stiffness since those are not functions of the step size. The accuracy results for verifying the tangent-stiffness calculation methods are summarized in Table~\ref{tab:ConvergenceStudy}. 
